---
title: "ICM Pipeline Comparisson"
author: "Sergio Gozalo"
date: "25 de febrero de 2021"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = setwd("/Users/Usuario/Desktop/Bioinformatica/Practicas/Practicas/Analysis/"))
```

## Loading necessary libraries

```{r}
library("vegan")
library("ggplot2")
library("tidyr")
library("dplyr")
```


## Table reading

```{r}
icm_cog_meta <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_COG.lengthNorm.metaGsizeNorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))
icm_cog_scg <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_COG.lengthNorm.SCGnorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))

icm_kegg_meta <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_KEGG.ko.lengthNorm.metaGsizeNorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))
icm_kegg_scg <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_KEGG.ko.lengthNorm.SCGnorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))

icm_pfam_meta <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_pfam.lengthNorm.metaGsizeNorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))
icm_pfam_scg <- t(read.table("functional.tables/EMOSE-GC_ICM_250bp_pfam.lengthNorm.SCGnorm.counts.tbl", header = TRUE, sep = "\t", row.names = 1))
```

## Bray-Curtis dissmilarity matrix

```{r}
#COG
icm_cog_meta_bray <- vegdist(icm_cog_meta, method="bray")
icm_cog_scg_bray <- vegdist(icm_cog_scg, method="bray")

#KEGG
icm_kegg_meta_bray <-vegdist(icm_kegg_meta, method="bray") 
icm_kegg_scg_bray <-vegdist(icm_kegg_scg, method="bray") 

#PFAM
icm_pfam_meta_bray <-vegdist(icm_pfam_meta, method="bray") 
icm_pfam_scg_bray <-vegdist(icm_pfam_scg, method="bray")
```

# MetaGSize vs SCG

## Comparing MetaGSize and SCG normalizations

```{r}
#Plots
plot(icm_cog_meta_bray, icm_cog_scg_bray, main = "COG: metaGsize vs SCG")
abline(0,1)

plot(icm_kegg_meta_bray, icm_kegg_scg_bray, main = "KEGG: metaGsize vs SCG")
abline(0,1)

plot(icm_pfam_meta_bray, icm_pfam_scg_bray, main = "PFAM: metaGsize vs SCG")
abline(0,1)

#Mantel test for correlation
mantel(icm_cog_meta_bray, icm_cog_scg_bray)
mantel(icm_kegg_meta_bray, icm_kegg_scg_bray)
mantel(icm_pfam_meta_bray, icm_pfam_scg_bray)
```

Both, plots and mantel tests, show a very high positive correlation.

## Comparisson of MetaGSize from different tables

```{r}
#Plots
plot(icm_cog_meta_bray, icm_kegg_meta_bray, main = "COG-meta vs KEGG-meta")
abline(0,1)
plot(icm_cog_meta_bray, icm_pfam_meta_bray, main = "COG-meta vs PFAM-meta")
abline(0,1)
plot(icm_pfam_meta_bray, icm_kegg_meta_bray, main = "PFAM-meta vs KEGG-meta")
abline(0,1)

#Mantel test for correlation
mantel(icm_cog_meta_bray, icm_kegg_meta_bray)
mantel(icm_cog_meta_bray, icm_pfam_meta_bray)
mantel(icm_pfam_meta_bray, icm_kegg_meta_bray)
```

Again, plots and mantel tests shows high correlation, that implies that results are consistent since different databases provide very similar results

## Comparisson of SCG from different tables

```{r}
#Plots
plot(icm_cog_scg_bray, icm_kegg_scg_bray, main = "COG-SCG vs KEGG-SCG")
abline(0,1)
plot(icm_cog_scg_bray, icm_pfam_scg_bray, main = "COG-SCG vs PFAM-SCG")
abline(0,1)
plot(icm_pfam_scg_bray, icm_kegg_scg_bray, main = "PFAM-SCG vs KEGG-SCG")
abline(0,1)

#Mantel test for correlation
mantel(icm_cog_scg_bray, icm_pfam_scg_bray)
mantel(icm_cog_scg_bray, icm_kegg_scg_bray)
mantel(icm_pfam_scg_bray, icm_kegg_scg_bray)
```

Once more, results show very high correlation, in this case is even greater than in the metaGSize.